Genome-wide changes in expression during inflorescence architecture development

### 2015-08-25 ms.Rmd
started nasty code for comparing published in situ results
bug in data.table split leading to lost data points'
stupid error calling expressed genes
added factor for facetting GSEA plot on TF category

## Patterns of expression of transcription families

@@

The patterns are not completely representative of all members of each gene family. For example, there are several MADS genes that have lower expression in the SM than in the RM, but expressed MADS genes were detected at a higher level overall in SM. Nevertheless, there are some notable modes of expression shared between different TF families. Several TF families, including bZIP and ABI3VP1, are strongly expressed in RM and lower in the other meristem types. Another group incluiding Squamosa binding proteins and Jumonji transcription factors is more weakly expressed in the RM but enriched in the PBM, suggesting a switch of expression between these two meristem types. Correspondingly, the difference between the RM and PBM samples was the most remarkable in the GSEA.

@@

>>>>

## Dynamic expression of transcription factor families

@@

The patterns are not completely representative of all members of each gene family. For example, there are several MADS genes that have lower expression in the SM than in the RM, but expressed MADS genes were detected at a higher level overall in SM. Nevertheless, there are some notable modes of expression shared between different TF families. Several TF families, including bZIP and ABI3VP1, are strongly expressed in RM and lower in the other meristem types. Another group incluiding Squamosa binding proteins and Jumonji transcription factors is more weakly expressed in the RM but enriched in the PBM, suggesting a switch of expression between these two meristem types. Correspondingly, the most pronounced difference in the GSEA was that between the RM and PBM samples.

@@

```{r f_reviewInSitu, fig.height = 8.661 / 4}
print(f_reviewInSitu)
```
